Manuscript title

### 2025-05-08 paper modification/CPB-tex-template/CPB Template-LaTeX/paper.tex
add new tex

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex}

\begin{document}
\begin{CJK*}{GBK}{song}

@@

\textbf{Example 1} A one-dimensional harmonic oscillator is described by the following equation:
\begin{eqnarray}
m_{\rm o}a=m_{\rm o}\frac{{\rm d}^2 x}{{\rm d}^2 t}=-k_{\rm s}x,
\end{eqnarray}
where $x$ and $a$ are the position and the acceleration of the oscillator, respectively, $m_{\rm o}$
is the mass of the oscillator, and $k_{\rm s}$ is the spring constant (subscripts ${\rm o}$ and ${\rm s}$ denote the oscillator and the spring, respectively).

@@

Tables are inserted in the center environment.

@@

\subsection*{5. References}

\textcolor[rgb]{0.98,0.00,0.00}{$\bullet$ Only published or accepted manuscripts should be included in this reference list;}

\textcolor[rgb]{0.98,0.00,0.00}{$\bullet$ References should all be cited in the main text by using command ucite (Chinese Physics B\ucite{1}) or cite (in Refs.~\cite{1,2,3,4});}

\textcolor[rgb]{0.98,0.00,0.00}{$\bullet$ Each reference item should contain one and only one publication;}

\textcolor[rgb]{0.98,0.00,0.00}{$\bullet$ References must be numbered in the order that they appear in the main text;}

\textcolor[rgb]{0.98,0.00,0.00}{$\bullet$ All authors of a publication should be listed, omission is not allowed unless there are more than 20 of them; \emph{et al.} should be used in the later case after the 3rd author to omit the others.}

Some reference examples are shown below.

\subsubsection*{Journal}

[1] Shahverdiev E M and Shore K A 2005 \emph{Phys. Rev. E } \textbf{71} 016201

[2] Wang J S, Feng J and Zhan M S 2010 \emph{Acta Phys. Sin.} \textbf{50} 299 (in Chinese)

\subsubsection*{Book}

[3] Murrell J N, Carter S, Farantos S C, Huxley P and Varandas A J C 1984 \emph{Molecular
Potential Energy Functions} (Chichester: John Wiley and Sons) p.~9

[4] Bloembergen N 1965 \emph{Nonlinear Optics}, 2nd edn. (New York: Benjamin) pp.~12--15

\subsubsection*{Conference publication}

[5] Tabbal A M, Merel P and Chaker M 1999 \emph{Proceedings of the {\rm 14}th International
Symposium on Plasma Chemistry}, August 2--6, 1999, Prague, Czech Republic, p.~1099

[6] Magen N, Kolodny A, Weiser U and Shamir N 2004 \emph{Proceedings of the International
Workshop on System Level Interconnect Prediction}, February 14--16, 2004, Paris, France, p.~7

\subsubsection*{arXiv}

[7] Latham T and Gershon T 2008 arXiv:0809.0872v1 [hep-ph]

\subsubsection*{Patent}

[8] Plank C J (U.S. Patent) 4 081 490 [1978-02-15]

\subsubsection*{Dissertation}

[9] Guo Z Y 2005 \emph{Optical Readout Infrared Imaging System at Room Temperature} (Ph.D. Dissertation) (Hefei: University of Science and Technology of China) (in Chinese)

>>>>

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex}
\bibliographystyle{iopart-num} 
\begin{document}
\begin{CJK*}{GBK}{song}

@@

\textbf{Example 1} A one-dimensional harmonic oscillator is described by the following equation:
%\begin{eqnarray}
\begin{equation}
m_{\rm o}a=m_{\rm o}\frac{{\rm d}^2 x}{{\rm d}^2 t}=-k_{\rm s}x,
\end{equation}
%\end{eqnarray}
where $x$ and $a$ are the position and the acceleration of the oscillator, respectively, $m_{\rm o}$
is the mass of the oscillator, and $k_{\rm s}$ is the spring constant (subscripts ${\rm o}$ and ${\rm s}$ denote the oscillator and the spring, respectively).

@@

Tables are inserted in the center environment\cite{tamm1959general}.

@@

\subsection*{5. References}
\bibliography{aipsamp_ADE}
